Contracts for Contracts

### 2023-04-27 paper.tex
add example

When specifying the spec of functions, two special variables are available
`msg.sender` the address of the caller and `block.timestamp` the current
block timestamp. 
\zz{How about other special variables, such as `block.chainid` and `tx.origin`?. Perhaps we could redesign a universal syntax for these variables in Section 2.5, where we discuss where to add the message sender}

\begin{lstlisting}
  # { msg.sender ... }
  NEED AN EXAMPLE USING THEM
\end{lstlisting}

@@

We can specify the contract for function arguments too:
\begin{lstlisting}
  # { f | {x | x < 0} -> {y | y > 0} }
  function map(int[] memory data, function (int) pure returns (int) f) { ... }
\end{lstlisting}
It might be too verbose -- so we can define those predicates separately for better readability/maintainability:
\begin{lstlisting}
  function greaterThanZero(int x) returns (bool) {
    return x > 0;
  }
  function smallerThanZero(int x) returns (bool) {
    return x < 0;
  }
  # { f | smallerThanZero -> greaterThanZero }
  function map(int[] memory data, function (int) pure returns (int) f) { ... }
\end{lstlisting}

Functions contracts can be higher-order -- it can take other function contracts
as part of the spec. For example
\begin{lstlisting}
  # TODO
  function f(function (function (int) returns (int) g) h) { ... }
\end{lstlisting}

@@

\wac{We may need an example here since the necessity to designate the callee function may not be obvious to reviewers.}

>>>>

When specifying the spec of functions, two special variables are available
`msg.sender` the address of the caller and `block.timestamp` the current
block timestamp. 
\zz{How about other special variables, such as `block.chainid` and `tx.origin`?. Perhaps we could redesign a universal syntax for these variables in Section 2.5, where we discuss where to add the message sender}
\url{https://docs.soliditylang.org/en/develop/units-and-global-variables.html#block-and-transaction-properties}

\begin{lstlisting}
  # { n | msg.value >= 1e15 * n }
  function buyTickets(int n) payable { ... }
\end{lstlisting}

@@

We can specify the contract for function arguments too:
\begin{lstlisting}
  # { f | {x | x < 0} -> {y | y > 0} }
  function map(int[] memory data, function (int) pure returns (int) f) { ... }
\end{lstlisting}
It might be too verbose -- so we can define those predicates separately for better readability/maintainability:
\begin{lstlisting}
  function greaterThanZero(int x) pure returns (bool) {
    return x > 0;
  }
  function smallerThanZero(int x) pure returns (bool) {
    return x < 0;
  }
  # { f | smallerThanZero -> greaterThanZero }
  function map(int[] memory data, function (int) pure returns (int) f) { ... }
\end{lstlisting}

Functions contracts can be higher-order -- it can take other function contracts
as part of the spec. For example
\zz{coooool!}
\begin{lstlisting}
  # TODO
  function f(function (function (int) returns (int) g) h) { ... }
\end{lstlisting}

@@

\wac{We may need an example here since the necessity to designate the callee function may not be obvious to reviewers.}
\zz{I guess we should educate the audience about the difference between low-level and high-level calls at the beginning of Section 2.4. I'll take care of this later.}
